Spatio-temporal estimates of HIV risk group proportions for adolescent girls and young women across 13 priority countries in sub-Saharan Africa

### 2022-07-09 src/docs_paper/appendix.Rmd
Add information criteria plot for multinomial to appendix #128
JWE suggests replacing .jpeg with .png #128

To fill: table and figure.

@@

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics{depends/fsw-logit-information-criteria.jpeg}}
    \caption{Logistic regression model performance, with the best performing model(s) according to each criteria shown as a square.}
    \label{fig:logistic-model-performance}
\end{figure}

@@

\begin{figure}
  \centering
  \makebox[\textwidth][c]{\includegraphics{depends/coverage.jpeg}}
  \caption{Probability integral transform (PIT) histograms (top row) and empirical cumulative distribution function (ECDF) difference plots (bottom row) for the final selected models. These plots are adapted from \citet{sailynoja2021graphical} and are an example of posterior predictive checks, see for example \citet[Chapter 6.1]{gelman2020bayesian}.}
  \label{fig:coverage}
\end{figure}

>>>>

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics{depends/model-comparison.png}}
    \caption{Multinomial regression model performance, with the best performing model(s) according to each criteria shown as a square.}
    \label{fig:multinomial-model-performance}
\end{figure}

To fill: table.

@@

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics{depends/fsw-logit-information-criteria.png}}
    \caption{Logistic regression model performance, with the best performing model(s) according to each criteria shown as a square.}
    \label{fig:logistic-model-performance}
\end{figure}

@@

\begin{figure}
  \centering
  \makebox[\textwidth][c]{\includegraphics{depends/coverage.png}}
  \caption{Probability integral transform (PIT) histograms (top row) and empirical cumulative distribution function (ECDF) difference plots (bottom row) for the final selected models. These plots are adapted from \citet{sailynoja2021graphical} and are an example of posterior predictive checks, see for example \citet[Chapter 6.1]{gelman2020bayesian}.}
  \label{fig:coverage}
\end{figure}

### 2022-07-09 src/docs_paper/paper.Rmd
JWE suggests replacing .jpeg with .png #128

```{r fig.cap="Surveys used in our analysis by year, survey type, sample size, and whether the survey included a question about transactional sex. \\label{fig:available-surveys}"}
knitr::include_graphics("depends/available-surveys.jpeg")
```

@@

```{r continental-map, fig.cap="The spatial distribution (posterior mean) of the AGYW risk group proportions in 2018. Countries in grey were not included in our analysis. \\label{fig:continental-map}"}
#' Note that the subnational borders look a bit overpowering when the quality of this is reduced
knitr::include_graphics("depends/3p1-continental-map.jpeg")
```

```{r within-between-country-variation, fig.cap="National (in white) and subnational (in color) posterior means of the risk group proportions. We used regions of sub-Saharan Africa defined according to the UN geocode (M49). \\label{fig:within-between-country-variation}"}
knitr::include_graphics("depends/3p1-within-between-country-variation.jpeg")
```

@@

```{r fig.cap="Percentage of new infections reached across all 13 countries, taking a variety of risk stratification approaches, against the percentage of at risk population required to be reached. \\label{fig:infections-reached}"}
knitr::include_graphics("depends/infections-reached.jpeg")
```

>>>>

```{r fig.cap="Surveys used in our analysis by year, survey type, sample size, and whether the survey included a question about transactional sex. \\label{fig:available-surveys}"}
knitr::include_graphics("depends/available-surveys.png")
```

@@

```{r continental-map, fig.cap="The spatial distribution (posterior mean) of the AGYW risk group proportions in 2018. Countries in grey were not included in our analysis. \\label{fig:continental-map}"}
#' Note that the subnational borders look a bit overpowering when the quality of this is reduced
knitr::include_graphics("depends/3p1-continental-map.png")
```

```{r within-between-country-variation, fig.cap="National (in white) and subnational (in color) posterior means of the risk group proportions. We used regions of sub-Saharan Africa defined according to the UN geocode (M49). \\label{fig:within-between-country-variation}"}
knitr::include_graphics("depends/3p1-within-between-country-variation.png")
```

@@

```{r fig.cap="Percentage of new infections reached across all 13 countries, taking a variety of risk stratification approaches, against the percentage of at risk population required to be reached. \\label{fig:infections-reached}"}
knitr::include_graphics("depends/infections-reached.png")
```
